\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-03-17 chapters/1_intro.tex
Update list of update rules and associated algs.
Small changes

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.pdf} % left bottom right top
\caption{\small 
Intro image: explain algorithm, main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

@@

\item In both approaches we can obtain the final segmentation by using a \textbf{graph clustering algorithm}
\item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
\item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
\item our contributions:
\begin{itemize}
\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
\item we propose several new clustering algorithms, among which one proved to be robust in our experiments (average linkage with must-not-link-edges)
\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and MC energy)

>>>>

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.pdf} % left bottom right top
\caption{\small 
Intro image: explain algorithm, main ideas and contributions \TODO{Update colormap with one with two colors only? Atm it can look like another segmentation}
\label{fig:intro_figure}}
\end{figure}

@@

\item In both approaches we can obtain the final segmentation by using a \textbf{graph clustering algorithm}
\item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
\item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
\item our contributions:
\begin{itemize}
\item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
\item new clustering algorithms on signed graphs
\item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and MC energy)

### 2019-03-17 chapters/3_algorithm.tex
Small changes

\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster. (the alg. will introduce them dynamically...)
\item Define contracted graph and edge contraction (explain Fig. 2)
\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e. a function of all the edge weights connecting the two clusters:
\begin{equation} \label{eq:linkage_criterion_def}
\begin{gathered}
\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
\end{gathered}
\end{equation}

@@

We consider a graph $\mathcal{G}(V,E,W)$ with associated signed edge weights, where each node initially represents one cluster.
The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters. Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \ref{fig:general_idea}b and \ref{fig:general_idea}c).

@@

Given an initial clustering $\Pi$ where each node of the original graph $\mathcal{G}$ represents its own cluster, the algorithm starts by initializing a contracted graph $\mathcal{G}'$ (see Definition \ref{def:contr_graph}) that will represent the clustering $\Pi$ at each iteration of the agglomeration. The algorithm then sorts all edges $e\in E$ by their absolute weight $|W(e)|$ in descending order in a priority queue, so that the most attractive and the most repulsive edges are processed first. It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated to $e_{uv}$, does the following. If the edge is attractive and $\tilde{w}>0$, then perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec. \ref{sec:contr_graph_and_CLC} and Fig. \ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update cannot-link relationships (see example in Fig. \ref{fig:algorithm_with_without_CLC}b from step 3 to 4). If, on the other hand, the edge $e_{uv}$ is repulsive and $\tilde{w}\leq 0$, then flag it as a cannot-link constraint if and only if the algorithm input-option \texttt{addCannotLink} is true and mutual exclusion relationships should be enforced.

@@

\subsection{Update rules and associated algorithms}
\begin{itemize}
\item In this section we will list some of the algorithms that can be described using the generalized algorithm we presented and define some new ones
\item In Table 1 we collected the update rules we tested and compared in this article (correspond to the simplest and cheapest ones to compute). Later we will mention more of them that were proposed in the literature.
\item In the special case of unsigned graphs (Table \ref{tab:linkage-criteria} column 1), the UGAC algorithm becomes simply a version of hierarchical clustering with different linkage criteria depending on the chosen update rule. It outputs one single cluster and it also defines an hierarchy of clusters during the merging process that can be associated to \UPDATE{a merging tree/  the hierarchical clustering dendrogram}... \TODO{Problem: sum does not trivially define an ultra-metric-distance...}  
\item In the literature there have been already several methods using cannot-link constraints for agglomerative clustering algorithms \TODO{repetition from related work}: for example, \cite{malmberg2011generalized} used initially fixed mutual exclusion relationships, whereas \cite{levinkov2017comparative} introduced them dynamically in an edge contraction algorithm for signed graphs, named Greedy Fixation (Table \ref{tab:linkage-criteria} row 1, \emph{sum}). At the same time, they also proposed a version of it without cannot link constraints (Greedy Additive Edge Contraction) and they compared both with other greedy and local-search algorithms for solving the multicut/correlation clustering problem.
\item Dynamically introduced cannot-link constraints were also proposed by \cite{wolf2018mutex}, that... \TODO{brief MWS description as efficient implementation of this update rule}. In the Supplementary material we show that the algorithm they present can be seen as a special case of UGACA with absolute maximum update rule (Table \ref{tab:linkage-criteria} row 2 - \emph{absolute maximum}) and that adding or not cannot-link constraints does not change the final clustering.
\item On the other hand, the signed graph versions of UGACA with update rules \emph{arithmetic mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}) are new algorithms that were never mentioned in the literature, \UPDATE{especially those with cannot-link constraints}.
\item In this article, we test and run a comparison of the five types of update rule listed in Table \ref{tab:linkage-criteria} (i.e. \emph{sum}, \emph{absolute mac}, \emph{arithmetic mean}, \emph{max} and \emph{min}), since \UPDATE{they they are the most commonly used and the cheapest to compute}. Nevertheless, UGACA can be easily generalized to include even more complex rules. For instance, \cite{nunez2013machine} proposes a learned version of update rule where a neural network updates the edge weights depending on edge and node features; another really common choice is to introduce a weight regularization depending on the size of the linked nodes (\cite{felzenszwalb2004efficient} and \cite{kardoostsolving} (unpublished...??), Thorsten..); 
\cite{funke2018large} on the other hand accumulate statistics for each \UPDATE{boundary between clusters} by keeping a discrete histograms of the edge weights and then computes quantiles from it.
\end{itemize}

>>>>

\item Given a clustering $\Pi$ and a graph $\mathcal{G}(V,E,W)$, the interaction between two clusters $S_1, S_2 \in \Pi$ is usually defined in terms of a \emph{linkage criterion}, i.e. a function of all the edge weights connecting the two clusters:
\begin{equation} \label{eq:linkage_criterion_def}
\begin{gathered}
\mathcal{L}(S_1,S_2) = \mathcal{L}(\mathcal{W})\quad \\
   \text{where} \quad \mathcal{W} = \{ W(e_{uv})| u\in S_1, v\in S_2 \}.
\end{gathered}
\end{equation}

\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster. (the alg. will introduce them dynamically)
\item Define contracted graph from given graph  $\mathcal{G}$ and clustering $\Pi$; explain edge contraction shown in Fig. 2

@@

We consider a graph $\mathcal{G}(V,E,W)$ with associated signed edge weights, where each node initially represents one cluster.
The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters. Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \ref{fig:intro_figure}b and \ref{fig:intro_figure}c).

@@

Given an initial clustering $\Pi$ where each node of the original graph $\mathcal{G}$ represents its own cluster, the algorithm starts by initializing a contracted graph $\mathcal{G}'$ (see Definition \ref{def:contr_graph}) that will represent the clustering $\Pi$ at each iteration of the agglomeration. The algorithm then sorts all edges $e\in E$ by their absolute weight $|W(e)|$ in descending order in a priority queue, so that the most attractive and the most repulsive edges are processed first. It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated to $e_{uv}$, does the following. If the edge is attractive and $\tilde{w}>0$, then merge the connected nodes and perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec. \ref{sec:contr_graph_and_CLC} and Fig. \ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update the cannot-link relationships (see example in Fig. \ref{fig:algorithm_with_without_CLC}b from step 3 to 4). If, on the other hand, the edge $e_{uv}$ is repulsive and $\tilde{w}\leq 0$, then flag it as a cannot-link constraint if and only if the algorithm input-option \texttt{addCannotLink} is true and mutual exclusion relationships should be enforced.

@@

\subsection{Update rules and associated algorithms}
\begin{itemize}
\item In this section we will list some of the algorithms that can be described using the generalized algorithm we presented and we will introduce some new ones.
\item In Table \ref{tab:linkage-criteria} we collected the update rules that we tested and compared in this article. Later we will mention more of them that were proposed in the literature.
\item In the special case of unsigned graphs (Table \ref{tab:linkage-criteria} column 1), the UGAC algorithm becomes simply a version of hierarchical clustering with different linkage criteria depending on the chosen update rule. It outputs one single cluster and it also defines an hierarchy of clusters during the merging process that can be associated to \UPDATE{a merging tree/  the hierarchical clustering dendrogram}... \TODO{Problem: sum does not trivially define an ultra-metric-distance...}  
\item In the literature there have been already several methods using cannot-link constraints for agglomerative clustering algorithms \TODO{repetition from related work}: for example, \cite{malmberg2011generalized} used initially fixed mutual exclusion relationships, whereas \cite{levinkov2017comparative} introduced them dynamically in an edge contraction algorithm for signed graphs, named Greedy Fixation (Table \ref{tab:linkage-criteria} row 1, \emph{sum}). At the same time, they also proposed a version of it without cannot link constraints (Greedy Additive Edge Contraction) and they compared both with other greedy and local-search algorithms for solving the multicut/correlation clustering problem.
\item Dynamically introduced cannot-link constraints were also proposed by \cite{wolf2018mutex}, that... \TODO{brief MWS description as efficient implementation of this update rule}. In the Supplementary material we show that the algorithm they present can be seen as a special case of UGACA with absolute maximum update rule (Table \ref{tab:linkage-criteria} row 2 - \emph{absolute maximum}) and that adding or not cannot-link constraints does not change the final clustering.
\item On the other hand, the signed graph versions of UGACA with update rules \emph{arithmetic mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}) are new algorithms that were never mentioned in the literature, \UPDATE{especially those with cannot-link constraints}.
\item In this article, we test and run a comparison of the five types of update rule listed in Table \ref{tab:linkage-criteria} (i.e. \emph{sum}, \emph{absolute mac}, \emph{arithmetic mean}, \emph{max} and \emph{min}), since \UPDATE{they they are the most commonly used and the cheapest to compute}. Nevertheless, UGACA can be easily generalized to include even more complex rules. For instance, \cite{nunez2013machine} proposes a learned version of update rule where a neural network updates the edge weights depending on edge and node features; another really common choice is to introduce a weight regularization depending on the size of the linked nodes (\cite{felzenszwalb2004efficient} and \cite{kardoostsolving} (unpublished...??), Thorsten..); 
\cite{funke2018large} on the other hand accumulate statistics for each \UPDATE{boundary between clusters} by keeping a discrete histograms of the edge weights and then computes quantiles from it.
\end{itemize}
